Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-02-24 analysis/paper.Rmd
Added headers
Added the methods section and updated the second replication goal in the introduction

In this work, we are attempting to confirm that the underlying data provided is the same as that used in the original study by replicating the figure showing the pair-wise correlation of all lance dimensions across the three underlying datasets (original study Fig 8). We are also attempting to replicate the original finding that there was no significant difference in mean shape between the three datasets by performing the Procrustes ANOVA analysis using the newer procD.lm function instead of the now deprecated procD.allometry function from the original paper.

@@

## Reproducing Figure 8 and associated analysis

@@

## Reproducing ANOVA analysis

@@

>>>>

In this work, we are attempting to confirm that the underlying data provided is the same as that used in the original study by replicating the figure showing the pair-wise correlation of all lance dimensions across the three underlying datasets (original study Fig 8). We are also attempting to replicate the original finding that there was found to be an association between overall centroid size and shape that could not be expained through site difference via an ANOVA analysis.

## Methods

The original analysis was conducted in an unspecified version of R. However, specific versions of geomorph(v3.0.6) and shapes(v1.2.3), two of the most important packages, were directly stated. Our reproduction attempt began with importing the packages explicitly identified in the paper as well as those required in the technical code.

<insert load packages block here>

Our next step was to set the working directory. Although a trivial step, the original code used setwd() and a static path string while our reproduction attempt opted to use the more robust here() library as shown below.

<insert set working dir here>

Next, we read in and shaped the data obtained from the ScieceDirect archive of the paper using the same code as the original paper, slightly modified to account for our modified approach to setting the working directory.

<insert read in data here>

With the R session properly configured, correct packages installed, and data loaded and shaped according to the paper and provided R file, we were then able to proceed with our attempt at replicating the correlation matrix of lance dimensions shown in Figure 8 of the original paper. This is where we encountered our first issue, as the code used to create the figure was not included in the R file. Instead a series of five corr() statements (shown below) comparing a subset of lance features were included with the resulting correlation coefficients included in the comments.

Pairwise correlations of lance features
cor(socket$socket_length,socket$sock_bdiam,use="pairwise.complete.obs") # 0.52
cor(socket$sock_bdiam,socket$sock_sdiam,use="pairwise.complete.obs")    # 0.52
cor(lances_M$width,lances_M$thickness,use="pairwise.complete.obs")      # 0.53
cor(blade$blade_length,blade$width,use="pairwise.complete.obs")         # 0.58
cor(blade$blade_length,blade$thickness,use="pairwise.complete.obs")     # 0.47

We then attempted to replicate the figure with the ggpairs() library and perform a visual comparison to Figure 8.

Finally, we attempted to replicate the original finding that there was found to be an association between overall centroid size and shape that could not be explained through site difference via an ANOVA analysis. This test was described on page 44 of the original paper as well as in the R document and relies on the procD.allometry() function from the geomorph package.

## Results

Unfortunately, the pairwise correlation coefficients noted in the comments were not the same as the ones shown in Figure 8. This inconsistiency made it more difficult to confirm the success of our replication attempt.

Luckily, we were able to replicate the finding that there was found to be an association between overall centroid size and shape that could not be explained through site difference via an ANOVA analysis on page 44 of the original paper

@@

### Reproducing Figure 8 and associated analysis

@@

### Reproducing ANOVA analysis

@@

## Conclusion

## References
